---
title: "P8105_hw5_jl5172"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
```

```{r,echo=T,message=F}
all_files<-list.files("./data/",full.names = T) 

df<- all_files %>% 
  map(read_csv)  #use map function to mapping read_csv in order to read all files in data folder


```

```{r}
for(i in 1:length(all_files)){  #categorize data by adding column named control arm
  if(i<=10){
   df[[i]]<-df[[i]] %>% 
     mutate(control_arm="Control",id=i)
  } else if (i>=11){
     df[[i]]<-df[[i]] %>% 
       mutate(control_arm="Experiment",id=i)
   }
}

df<-bind_rows(df)   
df<-df %>% 
  janitor::clean_names() %>% 
  as.tibble()
df
```


Spaghetti plot showing observations on each subject over time
```{r,fig.width =12}
df %>% 
  gather(key=week,value=data,week_1:week_8) %>% 
  ggplot(aes(x=week,y=data,color=control_arm, group =id))+
  geom_line()+geom_point(size=0.1)+
  facet_grid(~control_arm)+
  labs(title="Plot for Observations Over Weeks ",xlab="Week",ylab="Observation")

```

Comment:We can see from the plot that 
The observation data for control group are flutuating without showing any trend over weeks
whereas the trend for experimental group is increasing over weeks.

#Question 2
```{r,message=FALSE}
homicide<-read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
#reading csv from github
```

This dataset contains `r nrow(homicide)` observations and `r ncol(homicide)` variables. Observations denote cases of homicide over the past decade in 50 of the largest American cities.The dataset included the location of the killing-columns "city" and "state",whether an arrest was made--"disposition",basic demographic information about each victim--"victim_first","victim_last",victim_race","victim_age" and "victim_sex".



```{r}

  
```

Summarize homicide cases and unsolved homicide cases
```{r}
homicide_summary<- homicide %>%   
  mutate(city_state=str_c(city,state,sep=",")) %>% 
  group_by(city_state) %>% 
  summarise(homicide_cases=n())  #summarize all homicide cases

unsolved_summary<-homicide %>% 
  mutate(city_state=str_c(city,state,sep=",")) %>% 
  filter(disposition=="Closed without arrest"|disposition=="Open/No arrest") %>%   group_by(city_state) %>% 
  summarise(unsolved=n()) #summerize unsolved hoimicide cases
  
```

Combined summary for homcide cases
```{r}
combined_summary = 
  left_join(homicide_summary,unsolved_summary,by="city_state") #left_join,combined summary contain all rows from homicide_summary,if unsolved_summary do not have corresponding value, return NA)

 for(i in 1:51){
  if(is.na(combined_summary$unsolved[[i]])==T) {
    combined_summary$unsolved[[i]]<-0
  }
}    # use for loop to convert any NA data in unsolved column to 0

head(combined_summary)
```


Homcide prop.test for Baltimore
```{r}
Homicide_Baltimore<-combined_summary  %>% 
  filter(city_state=="Baltimore,MD") #find data of Baltimore using filter

Baltimore_prop_t<-prop.test(Homicide_Baltimore$unsolved,Homicide_Baltimore$homicide_cases) #Run prop.test for Baltimore

broom::tidy(Baltimore_prop_t) %>% 
select(estimate, conf.low, conf.high) #extracting parameters wanted

```

Prop.test of homicide/unsolved homicide cases for all 51 cities.
```{r}

combined_proptest <- map2(.x = combined_summary$unsolved, 
                          .y = combined_summary$homicide_cases, ~prop.test(.x, .y))   
#use map2 which can fit in two input columns and run prop.test for all cities


combined_proptest<-map_df(.x=combined_proptest,
         ~broom::tidy(.x) %>%    #tidy and select parameters wanted
  select(estimate,conf.low,conf.high))

combined_proptest<-combined_proptest %>% 
  mutate(city_state=combined_summary$city_state) %>%  # adding column city_state
  select(city_state,estimate,conf.low,conf.high)

head(combined_proptest)
```

Create a plot that shows the estimates and CIs for each city 
```{r,fig.width=10}
combined_proptest %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate, ymin = conf.low, ymax = conf.high,color=city_state)) +
    geom_point() +
    geom_errorbar() +
    #theme_bw() +
    theme(axis.text.x = element_text(angle = 90,size = 8)) +
  theme(legend.position = "none")+
  labs(x="City",y="Proportion Estimate",title="Proportion Estimates for All Cities")
  
```

